\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-07-25 to-do.tex
fix math in bookmarks issue in to-do.tex

\section{Make a bigger deal of the idea of $\ga$ decreasing function of $\tau$---move out of footnote}
\section{Big picture of which changes do what}
\vskip.2in
		\begin{tabular}{|l|c|c|}
			 & rigid & escape \\
			BS2005  & on-schedule (truthtelling): trivial; & need cost  \\
			 & off (repeated): optimal static if patient enough & \\
			$\ga(e)$ & on: trivial& no need, but revisit side payments\\
			 & off: mabye not b/c of lobby & \\
			$\ga(e,s)$ & ignore for now & is $s$ verifiable? def not w/$\ga(s,e)$
		\end{tabular}
\vskip.2in
\begin{itemize}
	\item Make sure this story is clear in text: I establish baseline tariff cap case, then add escape clause. We can already see a story of $\ldots$ emerge...
	\item Need to be clear when it is flexibility, enforcement, endogenous $\ga$ that screws things up. THEN need to bmake sure it comes out in paper
	\item May want to ditch repeated game part...
\end{itemize}

>>>>

\section{Make a bigger deal of the idea of \texorpdfstring{$\gamma$}{gamma} decreasing function of tariffs---move out of footnote}
Ethier 2012 for protection decreasing function of $\tau$ [NEED TO REVISIT IN TEXT]. ``The Political-Support Approach to Protection,'' Global Journal of Economics
	\begin{itemize}
		\item Making $W$ quadratic in $\ga$ such as $\ga - \ga^2$ gives a nice interior max
	\end{itemize}

\section{Big picture of which changes do what}
\vskip.2in
		\begin{tabular}{|l|c|c|}
			 & rigid & escape \\
			BS2005  & on-schedule (truthtelling): trivial; & need cost  \\
			 & off (repeated): optimal static if patient enough & \\
			$\ga(e)$ & on: trivial& no need, but revisit side payments\\
			 & off: mabye not b/c of lobby & \\
			$\ga(e,s)$ & ignore for now & is $s$ verifiable? def not w/$\ga(s,e)$
		\end{tabular}
\vskip.2in
\begin{itemize}
	\item Make sure this story is clear in text: I establish baseline tariff cap case, then add escape clause. We can already see a story of $\ldots$ emerge...
	\item Need to be clear when it is flexibility, enforcement, endogenous $\ga$ that screws things up. THEN need to bmake sure it comes out in paper
	\item May want to ditch repeated game part...
\end{itemize}
